---
title: "SGL Growth Models"
author: "Drew Walker"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

**This study aims to assess the effects of virtual social events on
Streetlight Gaming and Online Team patient, volunteer, and staff
comments on Discord.**

Streetlight is a palliative care peer support program at UF Health
Shands Children's Hospital. Streetlight Gaming and Online Team is an
online health community Discord server moderated by program staff and
volunteers to allow patients to connect with each other throughout
hospital admissions. In Discord, since 2018, we have hosted virtual
events ranging from Mario Kart tournaments to years-long Dungeons and
Dragons campaigns, to late night Among Us sessions. Since 2018, we have
also collected data on daily user comment totals, which we aggregate
into a large dataset containing data on all daily comment totals for all
patients, volunteers, and staff.

We also keep detailed event logs, documenting when events in the server
are facilitated and which players attended.

# Model Building

-   **Outcome**: User daily comments in Discord (recent comments)

-   **Level 1 Predictors**:

    -   Time/Individual repeated measures (Days in Discord)
    -   What about days since Discord started (for each date? equal
        across all users)
    -   Number of days since comment pull?

-   **Level 2 Predictors**:

    -   Patient, Volunteer, or Staff status,

-   **Level 3 Predictor**:

    -   Number of overall users in Discord

    -   number of comments in overall server on that day

    -   Number of days since comment was last pulled that day?

-   **Level 4 Predictors**:

    -   Presence of an event during that day

    -   Presence of seasonal event that day.

Data Description

-   71,833 daily comment total observations, filtered to 71725 due to
    issues with data carried over from users already in Discord server.

-   Total of 189 Users

    -   \# Patients

    -   \# Volunteers

    -   \# Staff

Although the data is daily comment totals, it is not regularly spaced in
timed intervals-- we run the code when we are able to on weekdays, but
due to concerns for patient data, we cannot schedule the code to be run
every day on a server

-   Average day difference ?

Events are also not occurring at regular intervals-- we schedule them at
the discretion of staff or patient need. I'm hoping this project, framed
as a quality improvement effort, will help program staff understand the
value in these events at driving community engagement, and be willing to
justify allocation of funds to these key moderator roles.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(table1)
library(nlme)
library(here)
here()
library(foreign)
library(gt)
library(redcapAPI)
library(scales)
library(lme4)
library(lubridate)
library(sjPlot)
library(sjmisc)
library(patchwork)
library(sjlabelled)
#install.packages('TMB', type = 'source')
library(TMB)
#Read in data from REDCap on discord user ids, names and status
options(scipen = 100)
redcap_api_url <- 'https://redcap.ctsi.ufl.edu/redcap/api/' 
#set options to allow us to access project files
#below is the token and urls
options(redcap_api_url)
APIToken <- read_csv("apitoken.csv", col_names = FALSE)
StreetlightDatabaseToken <- as.character(APIToken[1,1])
rcon <- redcapConnection(redcap_api_url, token = StreetlightDatabaseToken)
REDCapData_Patients <- exportRecords(rcon,labels = FALSE)


```

# Load in data from REDCap/last SGL data pull

<https://rpsychologist.com/r-guide-longitudinal-lme-lmer>

```{r SGL-data}
library(haven)
load("sgl_comments_data.Rda")

# output for hlm to get equation
hlm_snip <- firstday_set_filtered %>% 
  head(n = 600)

write_csv(hlm_snip, "sgl_snip.csv")
# Extra fun bc hlm doesn't work well with csv?
write.dta(hlm_snip, "sgl_snip.dta")

tmp <- tempfile(fileext = ".xpt")
write_xpt(hlm_snip, tmp)
write_sav(hlm_snip, "hlm_snip.sav")


library(nlme)
library(lme4)
#firstday_set$days_since_discord_first_comment<- #as.numeric(str_remove(firstday_set$days_since_discord_first_comme#nt, " days"))
#firstday_set$record_id <- as.factor(firstday_set$record_id)

# After first visualization, realize we need to remove data from 2019-01-24, because it caught existing discord users who were in server prior to data being collected. 

# Also after 2019-09-16 due to error in code that produced negative value
#firstday_set_filtered <- firstday_set %>% 
#  filter(date != "2019-01-24") %>% 
#  filter(date !="2019-09-16") %>% 
#  left_join(daily_summaries, by = "date")

#save(firstday_set_filtered,file="sgl_comments_data.Rda")

sgl_descriptives_df <- firstday_set_filtered %>% 
  distinct(record_id,status, .keep_all = TRUE)

date_list <- as.factor(firstday_set_filtered$date)

unique_date_list <- as.character(date_list) %>% 
  unique() %>% 
  as.Date()

TotalCommentStatusSummary <- firstday_set_filtered %>% 
  filter(date == "2022-01-19") %>% 
  group_by(status) %>% 
  summarise(status_message_count = sum(message_count))
TotalCommentStatusSummary <- TotalCommentStatusSummary %>% 
  ungroup() %>% 
  mutate(total_messages = sum(status_message_count),
         percentage_messages = ((status_message_count/total_messages)*100))

#Tables 
totalstatustable <- gt(TotalCommentStatusSummary)
totalstatustable




sgl_descriptives_df$status <- as.factor(sgl_descriptives_df$status)
table1(~status, data = sgl_descriptives_df)
# Recent comments by status 
table1(~recent_comments|status, data = firstday_set_filtered)

days_since_df <- firstday_set_filtered %>% 
  filter(date == "2022-01-19") %>% 
  distinct(record_id, .keep_all = TRUE)
table1(~days_since_discord_first_comment|status, data = days_since_df)

# Now we joined daily overall server summaries, which gives us
# users in discord, day's total discord comments, and active users
# Plot LOESS curve

plot_obs <- ggplot(data=firstday_set_filtered,         
                   aes(x = days_since_discord_first_comment,
                       y = recent_comments, group = record_id,color=status))+
  geom_line()+
  #adding lines to plot
                   theme_classic() + 
  scale_x_continuous(name = "Day since first comment")+
                   scale_y_continuous(name = "Daily Comments") 
plot_obs

plot_facet <- ggplot(data = firstday_set_filtered, aes(days_since_discord_first_comment,recent_comments))+
         geom_line(aes(color = status))+
  ggtitle('Daily commenting trends for Streetlight Gaming and Online Team, January 2019-2022')+
  theme_classic() +
  facet_wrap(~ record_id)
plot_facet

ggsave('sgl_facet.png', width = 50, height = 50, units = "in", limitsize = FALSE)

# Facet by status 

plot_facet_status <- ggplot(data = firstday_set_filtered, aes(days_since_discord_first_comment,recent_comments))+
         geom_line(aes(color = status))+
  ggtitle('Daily commenting trends for Streetlight Gaming and Online Team, January 2019-2022')+
  theme_classic() +
  facet_wrap(~ status)
plot_facet_status

ggsave('sgl_facet_status.png', width = 10, height = 10, units = "in", limitsize = FALSE)


null <- lme(recent_comments ~ days_since_discord_first_comment*status, random = ~ days_since_discord_first_comment | record_id, data=firstday_set_filtered, na.action = na.omit)

summary(null)
```

```{r, pt-descriptives}
# make today be the last day of data collection
SGLPatientsREDCap <- REDCapData_Patients %>% 
  group_by(record_id) %>% 
  fill(bday,deceased) %>% 
  mutate(team_cancer = unclass(first(project_team___1)),
    team_cf = unclass(first(project_team___2)),
    team_transplant = unclass(first(project_team___3)),
    team_sicklecell = unclass(first(project_team___4)),
    team_autoimmune = unclass(first(project_team___5)),
    team_gi = unclass(first(project_team___6)),
    team_other = unclass(first(project_team___7)),
    predicted_project_team = first(predicted_project_team)) %>% 
  pivot_longer(cols = starts_with("team_"),names_to = "project_team", values_to = "team_value", values_drop_na = TRUE) %>%
  select(record_id, id,discord_user,status,bday,deceased,sgl_study_eligible,predicted_project_team,project_team,preferred_gender,team_value) %>% 
  fill(discord_user,status,bday,deceased,sgl_study_eligible,predicted_project_team,project_team,preferred_gender) %>% 
  filter(team_value == "2") %>% 
  distinct(record_id, .keep_all = TRUE)

today <- as.Date(Sys.Date())
intervalbday <- SGLPatientsREDCap$bday %--% today
SGLPatientsREDCap$age <- intervalbday
patients_only <- sgl_descriptives_df %>% 
  filter(status == "Patient")
patient_list <- patients_only %>% 
  distinct(record_id)
patient_descriptives1 <- left_join(patient_list,SGLPatientsREDCap, by = "record_id") 

patient_descriptives <- patient_descriptives1 %>% 
  filter(is.na(deceased)|deceased != "Yes")

patient_descriptives$age <- as.numeric(patient_descriptives$age)/31536000

patient_descriptives$project_team <- as.factor(patient_descriptives$project_team)
patient_descriptives$project_team <- relevel(patient_descriptives$project_team, ref = "team_other")

table1(~age + deceased + predicted_project_team + project_team + preferred_gender, data = patient_descriptives)
```

# EDA Visualization

-   Need to check for missingness among predictors to be able to compare
    models across unconditional, etc.

```{r visualization}
plot<- ggplot(firstday_set_filtered, aes(x=date, y=recent_comments, color = status)) + 
  geom_line()+
  scale_y_continuous(name="Recent Comments")+
  theme_classic()+
  ggtitle("Daily Comments by Streetlight Status, Jan 2019-Jan 2022")
plot
```

## Event list

-   First, we qualitatively analyzed the event list to remove any
    non-patient events in the server. The SGL recruit log utilized for
    the events would often contain admin or server feature changes. We
    wanted to make sure this list was only providing data on when staff,
    volunteer, or patient-facilitated events occurred.

-   Seasonal events

    -   Summer Games

        -   Need to go back and make sure we input every event and the
            exact dates-- check Discord

        -   Check for events

            -   Find event for 6/3/2020

            -   Find date for Jackbox Game Night (Somewhere between
                1/8/2021-1/13/2021

            -   May try to truncate data starting at 10/4/2019 instead
                to test if no time to resolve data qual issues
                


```{r event-log-and-variable-transforming}
event_log <- read_csv("DeIdentified Event log.csv")

event_log$`Event Date` <- as.Date(event_log$`Event Date`, format = "%m/%d/%Y" )
  
event_log_clean <- event_log %>%   
  mutate(event_present = 1) %>% 
  rename(date = `Event Date`) 
# Seasonal events
seasonal_events <- read_csv("seasonal_events.csv")
seasonal_events$date <- as.Date(seasonal_events$date, format = "%m/%d/%Y" ) 
seasonal_events <- seasonal_events %>% 
  drop_na()
#266 days of seasonal events -- where patients engaged in challenges 


event_and_comment_df <- left_join(firstday_set_filtered,event_log_clean, by = "date")

# replace NA with 0 for days without events
event_and_comment_df$event_present[is.na(event_and_comment_df$event_present)] <- 0
event_and_comment_df$event_present <- as.factor(event_and_comment_df$event_present)
event_and_comment_df <- event_and_comment_df %>%
  mutate(day_of_week = wday(date),
         years_since_discord = days_since_discord_first_comment/365)

event_and_comment_df$day_of_week <- factor(event_and_comment_df$day_of_week, ordered = FALSE)

event_and_comment_df_descriptives <- left_join(event_and_comment_df,patient_descriptives, by = "record_id")
# join in seasonal events
event_and_comment_df_descriptives_2 <- left_join(event_and_comment_df_descriptives,seasonal_events, by = "date")
#make non seasonal event days 0
event_and_comment_df_descriptives_2$seasonal_event[is.na(event_and_comment_df_descriptives_2$seasonal_event)] <- 0
event_and_comment_df_descriptives_2$seasonal_event <- as.factor(event_and_comment_df_descriptives_2$seasonal_event)
event_and_comment_df_descriptives_2 <- event_and_comment_df_descriptives_2 %>% 
  mutate(commented_that_day = case_when(recent_comments >0 ~ "1", 
                                        TRUE ~ "0"))
patients_only1 <- event_and_comment_df_descriptives_2 %>% 
  filter(status.x == "Patient") %>% 
  filter(deceased != "Yes")

# Top users at 1-19-2022, assign quartiles for rank in total comments
patient_comment_total <- days_since_df %>% 
  select(record_id, message_count) 
patient_comment_total$quartile <- as.factor(ntile(patient_comment_total$message_count, 4))

patients_only2 <- left_join(patients_only1,patient_comment_total,by="record_id")
patients_only <- patients_only2 %>% 
  mutate(years_squared = years_since_discord^2,
         years_cubed = years_since_discord^3)

event_plot <- ggplot(patients_only, aes(x=date, y=event_present)) + 
  geom_point(na.rm = T,
             color = "black",
             fill = "#69b3a2",
             size = .25,
             alpha = .10)+
  theme_classic()+
  ggtitle("Daily Events in SGOT, Jan 2019-Jan 2022")
event_plot
seasonal_plot <- ggplot(patients_only, aes(x=date, y=seasonal_event)) + 
   geom_point(na.rm = T,
             color = "orange",
             fill = "orange",
             shape = 22,
             alpha = .1)+
  theme_classic()+
    ggtitle("Seasonal Events in SGOT, Jan 2019-Jan 2022")
seasonal_plot

active_users_plot <- ggplot(patients_only, aes(x=date, y=active_users)) + 
  geom_line(color = "forest green")+
  theme_classic()+
    ggtitle("Daily Active Users in SGOT, Jan 2019-Jan 2022")
active_users_plot



library(patchwork)
plot/event_plot/seasonal_plot/active_users_plot
ggsave('comments_and_events.png', width = 10, height = 10, units = "in", limitsize = FALSE)

table1(~recent_comments + years_since_discord, data = patients_only)
```

# Unconditional Means, Unconditional Growth Models , and invididual covariate conditional growth models

```{r unconditional-means}
unconditional_means = lmer(recent_comments ∼ 1+ (1|record_id), data = patients_only, REML=FALSE)

summary(unconditional_means)
# Unconditional growth
unconditional_growth = lmer(recent_comments ∼  years_since_discord + (years_since_discord|record_id), data = patients_only, REML=FALSE)

summary(unconditional_growth)

individual_covariates = lmer(recent_comments ∼  years_since_discord + age + preferred_gender + project_team + (years_since_discord|record_id), data = patients_only, REML=FALSE)

summary(individual_covariates)



tab_model(unconditional_means, unconditional_growth, individual_covariates, dv.labels = c("Unconditional Means Model","Unconditional Growth", "Individual Covariates"), show.aic = TRUE, show.dev = TRUE)
```

# Conditional Growth Models

## Individual-level covariates


age + preferred_gender + project_team



## Event fixed

```{r conditional-growth-event-models}
event_model = lmer(recent_comments ∼  years_since_discord*event_present + (years_since_discord|record_id), data = patients_only, REML=FALSE)

summary(event_model)

seasonal_model = lmer(recent_comments ~ years_since_discord*seasonal_event + (years_since_discord|record_id), data = patients_only, REML=FALSE)

summary(seasonal_model)

both_model_linear = lmer(recent_comments ~  years_since_discord*event_present + active_users + years_since_discord*active_users + (years_since_discord|record_id), data = patients_only, REML=FALSE)


tab_model(unconditional_means, unconditional_growth, event_model, seasonal_model,both_model_linear, dv.labels = c("Unconditional Means Model","Unconditional Growth", "Conditional Day Event Model","Conditional Seasonal Event Model","Daily events and active users model"), show.aic = TRUE, show.dev = TRUE)

# Years or without 


```


## Other active users models, treating active users as outcome

* likely that events may cause more active users, in which case we shouldn't control for it since it's a mediator to total comments? 

* But it also is part of the OHC channel richness

```{r conditional-growth-active-user-models}
active_users_model = lmer(recent_comments ∼  years_since_discord*active_users + users_in_discord + (years_since_discord|record_id), data = patients_only, REML=FALSE)

active_users_outcome = (lm(active_users~event_present + seasonal_event, data = patients_only))

tab_model(active_users_model, dv.labels = c("Active Users Model"), show.aic = TRUE, show.dev = TRUE)


active_users_outcome
tab_model(active_users_outcome, dv.labels = c("Active Users As Predicted by Events"), show.aic = TRUE, show.dev = TRUE)

```


## Day of week simple linear regression

```{r day-of-week}
day_model <- lm(recent_comments ~ day_of_week + years_since_discord, data =patients_only)
summary(day_model)
```

No significant effects identified for day of week in model 

Descriptives at each level


```{r descriptives}
TotalCommentStatusSummary <- patients_only %>% 
  filter(date == "2022-01-19") 
sum(TotalCommentStatusSummary$message_count.x)
TotalCommentStatusSummary

```

