---
title: "SGLReportwithREDCap"
author: "Drew Walker"
output:
  html_document: default
  pdf_document: default
  word_document: default
date: "`r format(Sys.time(), '%d %B, %Y')`"
---
```{r setup, include=FALSE}
library(devtools)
library(pkgbuild)
library(rlang)
library(purrr)
library(tidyverse)
library(lubridate)
library(RColorBrewer)
library(knitr)
library(yaml)
library(rmarkdown)
library(ggplot2)
library(here)
library(patchwork)
library(gt)
library(redcapAPI)
library(scales)
library(fuzzyjoin)
library(ggrepel)
#Read in data from REDCap on discord user ids, names and status
options(scipen = 100)
redcap_api_url <- 'https://redcap.ctsi.ufl.edu/redcap/api/' 
#set options to allow us to access project files
#below is the token and urls
options(redcap_api_url)

APIToken <- read_csv("apitoken.csv", col_names = FALSE)
StreetlightDatabaseToken <- as.character(APIToken[1,1])
rcon <- redcapConnection(redcap_api_url, token = StreetlightDatabaseToken)

VolToken <- read_csv("volunteertoken.csv", col_names = FALSE)
StreetlightVolunteerToken <- as.character(VolToken[1,1])
vcon <- redcapConnection(redcap_api_url, token = StreetlightVolunteerToken)
```

```{r dataload-players, include=FALSE}
#Filtering to just the SGL data on patients involved in SGL 
files <- dir(path = getwd(), pattern = "Players.", full.names = TRUE)
tbl <- sapply(files, read_csv, simplify = FALSE) %>%
  bind_rows(.id = "fileid")
#Then after reading in and uploading, can we move these files to an archive? 
#format for merging
cuttbl <- tbl %>%
  select(-fileid,-xp, -level,-X1) %>% 
  arrange(desc(date))
cuttbl$id <- as.character(cuttbl$id)
```




```{r dataload-from-REDCap, include=FALSE}
#format for merging 
#REPLACE WITH REDCAP PULL
REDCapData_Patients <- exportRecords(rcon,labels = FALSE)

patient_comments <- REDCapData_Patients %>% 
  filter(redcap_repeat_instrument == "sgl_comments") %>% 
  select(comments_user,comments_id,comments_message_count,comments_date) %>% 
  rename(user = comments_user,
         id = comments_id,
         message_count = comments_message_count,
         date = comments_date)
patient_comments$date <- as.Date(patient_comments$date)
patient_comments <- patient_comments %>% 
    arrange(desc(date))
patient_comments$id <- as.character(patient_comments$id)
```

```{r volunteer-redcap-data-load, echo = FALSE}
REDCapData_Volunteers <- exportRecords(vcon,labels = FALSE)

volunteer_comments <- REDCapData_Volunteers %>% 
  filter(redcap_repeat_instrument == "sgl_comments") %>% 
  select(comments_user,comments_id,comments_message_count,comments_date) %>% 
  rename(user = comments_user,
         id = comments_id,
         message_count = comments_message_count,
         date = comments_date)
volunteer_comments$date <- as.Date(volunteer_comments$date)
volunteer_comments <- volunteer_comments %>% 
    arrange(desc(date))
volunteer_comments$id <- as.character(volunteer_comments$id)
```

```{r, combine-redcap-volunteers-and-patients, echo = FALSE}
sglhistory <- bind_rows(patient_comments,volunteer_comments)
```


```{r recent-players-data-and-history-merge, include=FALSE}
#combine recent files with history
megatbl <- bind_rows(cuttbl,sglhistory) %>% 
  distinct() %>% 
  arrange(desc(date))

# CREATE SGL DATASET With last_message count, recent comments ------------------------------------------------------
datedtbl <- megatbl %>% 
  group_by(id) %>% 
  mutate(last_date = dplyr::lead(date, order_by = id),
         last_message_count = lead(message_count, order_by = id)) 
datedtbl$last_message_count <- replace(datedtbl$last_message_count, is.na(datedtbl$last_date),0)
datedtbl <- datedtbl %>% 
  mutate(recent_comments = (message_count - last_message_count),
         time_interval = as.duration(last_date %--% date),
         daily_comments = recent_comments %/% (time_interval %/% 86400)) %>% 
  ungroup()
#Datacleaning step necessary in preserving accurate id values
datedtbl$id <- as.character(datedtbl$id)
```

```{r, REDCapDataPull-naming-patients-and-vols-and-roles, include=FALSE}
SGLPatientsREDCap <- REDCapData_Patients %>% 
  group_by(record_id) %>% 
  fill(p_full_name,vol_preferred_name,bday,deceased) %>% 
    ungroup() %>% 
  filter(id != "NA",
         record_id != "NA") %>% 
  select(record_id,p_full_name, vol_preferred_name, id, discord_user,status,bday,deceased,sgl_study_eligible) %>% 
  rename(player_name = p_full_name)
today <- as.Date(Sys.Date())
intervalbday <- SGLPatientsREDCap$bday %--% today

#Now pull in volunteer information

REDCapData_Volunteers <- exportRecords(vcon,labels = FALSE)

#New SGL Repeated Form version
SGLVolunteers <- REDCapData_Volunteers %>% 
  group_by(record_id) %>% 
  fill(v_full_name) %>% 
  ungroup() %>% 
  filter(discordd_id != "NA",record_id != "NA") %>% 
  select(record_id,v_full_name, discordd_id, discord_userr,status) %>% 
  rename(player_name = v_full_name,
         id = discordd_id,
         discord_user = discord_userr,
         vol_record_id= record_id) %>% 
  mutate(record_id = paste("V",vol_record_id))
SGLVolunteers$id <- as.character(SGLVolunteers$id)

SGLPatientsMerge <- SGLPatientsREDCap %>% 
  select(id, discord_user, player_name,status,record_id) 

SGLRecruitLogMaster <- bind_rows(SGLPatientsMerge,SGLVolunteers)
datedtblnames <- full_join(datedtbl,SGLRecruitLogMaster, by = "id") %>% 
  group_by(id)
```

```{r, dataset merge, include=FALSE}
#Merge compiled Discord Information with Gaming League Recruit Log Data

# CREATING DAILY TREND DATAFRAME ------------------------------------------
day <- first(datedtblnames$date)
last_day <- day - 1
last_week_day <- day - 7
last_month_day <- day -31
last_year_day <- day - 365
#recent_pull: A cut of the datedtblnames with the most recent current total comment values
recent_pull <- datedtblnames %>% 
  slice(which.max(as.Date(date)))
recent_pull <- recent_pull %>% 
  arrange(desc(recent_comments))
#Fixing SGL IDs/Users

recent_pull_correct_ids <- recent_pull %>% 
  filter(date == day) %>% 
  select(user,id)
#CORRECTING IDs for OLD SGL, RECALCULATING, adding current user to be able to look back 
datedtbl_correct_ids <- stringdist_inner_join(datedtbl,recent_pull_correct_ids, by = "id", max_dist = 3)
datedtbl <- datedtbl_correct_ids %>% 
  select(-id.x) %>% 
  rename(id = id.y,
         user = user.x,
         user_current = user.y) %>% 
  group_by(id) %>% 
  mutate(last_date = dplyr::lead(date, order_by = id),
         last_message_count = lead(message_count, order_by = id)) 
datedtbl$last_message_count <- replace(datedtbl$last_message_count, is.na(datedtbl$last_date),0)
datedtbl <- datedtbl %>% 
  mutate(recent_comments = (message_count - last_message_count),
         time_interval = as.duration(last_date %--% date),
         daily_comments = recent_comments %/% (time_interval %/% 86400)) %>% 
  ungroup()
#JOIN WITH REDCAP NAMES
datedtblnames <- full_join(datedtbl,SGLRecruitLogMaster, by = "id") %>% 
  group_by(id)

#LAST PULL: Let's make a quick dataset with just the active_users_today
active_users_today <- recent_pull %>% 
  filter(recent_comments != 0)
#LAST WEEK: active_users_last_week
active_users_last_week <- datedtblnames %>% 
  filter(date > last_week_day) %>% 
  filter(recent_comments != 0) %>% 
  mutate(
    mean_comments = mean(recent_comments),
    total_comments_week = sum(recent_comments)) %>% 
  filter(date == as.Date(max(date)))
#LAST MONTH: active_users_last_month
active_users_last_month <- datedtblnames %>% 
  filter(date > last_month_day)%>% 
  filter(recent_comments > 0) %>% 
  mutate(
    mean_comments = mean(recent_comments),
    total_comments_month = sum(recent_comments)) %>% 
  filter(date == as.Date(max(date)))
# SUMMARY TABLES ----------------------------------------------------------
#daily_summaries is a combination of multiple datapoint summaries, number of active users, etc 
#total_users_by_date is a summary df (date and the total number of users on Discord. Not active, just that they have it)
total_users_by_date <- datedtblnames %>% 
  group_by(date) %>% 
  summarise(
    users_in_discord = n()
  )
#total_active_users_by_date represents the total active users for each date.
total_active_users_by_date <- datedtblnames %>% 
  group_by(date) %>% 
  filter(recent_comments != 0) %>% 
  summarise(
    recent_comments_total = sum(recent_comments, na.rm = TRUE),
    active_users = n())

daily_summaries <- merge(total_users_by_date,total_active_users_by_date)
month_daily_summaries <- daily_summaries %>% 
  filter(date > last_month_day)
#The issue causing the jump is that there is a disconnect between the correct ID for these patients
#So, we need to come up with a comprehensive list of all users with their correct ids, then merge that based on their username into datedtbl
```


```{r, firstday-code, echo = FALSE}
#This code is able to calculate the days since joining discord for every comment pull date. Will be helpful to build into REDCap upload. 
firstday_set <- datedtblnames %>% 
  group_by(record_id) %>% 
  mutate(first_day_in_discord = min(date),
         days_since_discord_first_comment = date - first_day_in_discord)
```


## SGL Social Engagement

This is a report meant to describe the daily commenting trends and active players in the Streetlight Gaming League.
```{r plots, echo=FALSE}
#This is the comment active users since March 23rd
#uses active users as dataframe
p_yesterday_comments_user_bar <- ggplot(data = active_users_today, aes(reorder(user, recent_comments), y = recent_comments, fill = user, label = recent_comments))+
  geom_col(show.legend = FALSE,
           width = 1)+
  geom_text(nudge_y = .25)+
  labs(x = NULL, y = NULL,
       title = "Yest. Comments by User",
       subtitle = (paste(last_day,"to",day, sep = " "))) + 
  coord_flip()+
    theme_classic()

#Comments per Status Plot from Yesterday's server data
#Dataframe: active_users_today 
p_status_yesterday_comments <- ggplot(data = active_users_today, aes(reorder(status, recent_comments), y = recent_comments, fill = status))+
  geom_col(show.legend = FALSE,
           width = 1)+
  labs(x = NULL, y = NULL,
       title = "Yesterday's Comments by SL Status",
       subtitle = paste(last_day,"to",day, sep = " "))+
  coord_flip()+
    theme_classic()

#let's do it with names
p_yesterday_comments_name_bar <- ggplot(data = active_users_today, aes(reorder(player_name, recent_comments), y = recent_comments, fill = status, label = recent_comments))+
  geom_col(show.legend = TRUE,
           width = 1)+
  geom_text(nudge_y = .25)+
  labs(x = NULL, y = NULL,
       title = "Yest. Comments by Status and Name",
       subtitle = (paste(last_day,"to",day, sep = " "))) + 
  coord_flip() +
    theme_classic()

#Plot for Daily Comments Totals Last Month 
#Dataframe: monthly_daily_summaries
p_month_recent_comments_totals <- ggplot(month_daily_summaries, aes(date, recent_comments_total, fill = date, label = recent_comments_total))+
  geom_col(show.legend = FALSE)+
  geom_text(nudge_y = 4)+
  labs(x = NULL, y = NULL)+
  ggtitle('Total Comments Per Day')+
  ylim(0,250)+
  theme_classic()

#Plotting Trends in Active Users
p_month_active_users <- ggplot(month_daily_summaries, aes(date, active_users, fill = date, label = active_users))+
  geom_col(show.legend = FALSE)+
  geom_text(nudge_y = 1)+
  labs(x = NULL, y = NULL)+
  ggtitle('SGL Daily Active Users')+
    theme_classic()


p_timeline_active_users <- ggplot(daily_summaries, aes(date, active_users, label = active_users))+
  geom_point(show.legend = FALSE)+
  geom_smooth(method = 'lm')+
  labs(x = NULL, y = NULL)+
  ggtitle('SGL Daily Active Users Since Jan 24, 2019')+
  scale_x_date(date_breaks = "2 months", date_labels = "%b-%y")+
    theme_classic()


p_timeline_daily_comments_totals <- ggplot(daily_summaries, aes(date, recent_comments_total))+
  geom_point()+
    geom_smooth(method = 'lm')+
  labs(x = NULL, y = NULL)+
  ggtitle('Total Comments Per Day since Jan 24, 2019')+
  scale_x_date(date_breaks = "2 months", date_labels = "%b-%y")+
    ylim(0,300)+
    theme_classic()


#Plotting Trends in Total Discord Server Members
p_timeline_discord_server_members <- ggplot(daily_summaries, aes(date, users_in_discord)) +
  geom_point()+
    geom_smooth(method = 'lm')+
  labs(x = NULL, y = NULL, title = "Discord Members since Jan 24, 2019", caption = "Flat line from 2020-02-recently = Mee6 code page limit")+
  scale_x_date(date_breaks = "2 months", date_labels = "%b-%y")+
    ylim(0,150)+
    theme_classic()


#Combining graphs for nice visualizations
p_month_active_users
p_month_recent_comments_totals
p_status_yesterday_comments
p_yesterday_comments_user_bar
p_yesterday_comments_name_bar
p_timeline_active_users
p_timeline_daily_comments_totals
p_timeline_discord_server_members
```

##Active Users Since Last Week 
This graph gives a sum of the comments made by users active in the last week in sgl.  
```{r usersonlylastweek, echo = FALSE}
p_active_week <- ggplot(data = active_users_last_week, aes(reorder(user, total_comments_week), y = total_comments_week, fill = user, label = total_comments_week))+
  geom_col(show.legend = FALSE,
           width = 1)+
  geom_text(aes(label = total_comments_week))+
  labs(x = NULL, y = NULL,
       title = "Last Week's Comments by User",
       subtitle = paste("From",last_week_day,"to",day, sep = " ")) +
  coord_flip()+
  theme_classic()
```
##Active Users Last Week with Names and Status
This will give us the player's names also
```{r userslastweekwithnamesandstatus, echo = FALSE}
p_active_week_names <- ggplot(data = active_users_last_week, aes(reorder(player_name, total_comments_week), y = total_comments_week, fill = status, label = total_comments_week))+
  geom_col(show.legend = TRUE,
           width = 1)+
  geom_text(aes(label = total_comments_week))+
  labs(x = NULL, y = NULL,
       title = "Last Week's Comments by Name/Status",
       subtitle = paste(last_week_day,"to",day, sep = " "))+
  coord_flip()+
  theme_classic()
p_active_week
p_active_week_names
```


##Active Users Since Last Month

This graph represents the total number of comments of all active players in the last month, by username. 

```{r userslastmonth, echo = FALSE}
p_active_month <- ggplot(data = active_users_last_month, aes(reorder(user, total_comments_month), y = total_comments_month, fill = user, label = total_comments_month))+
  geom_col(show.legend = FALSE,
           width = 1)+
  geom_text(aes(label = total_comments_month))+
  labs(x = NULL, y = NULL,
        title = "Last Month's Comments by User",
       subtitle = paste(last_month_day,"to",day, sep = " "))+
  coord_flip()+
  theme_classic()
p_active_month
```
##Active Patients, Volunteers, and Staff from Last Month
```{r userslastmonthwithnames, echo = FALSE}
p_active_month_names <- ggplot(data = active_users_last_month, aes(reorder(player_name, total_comments_month), y = total_comments_month, fill = status, label = total_comments_month))+
  geom_col(show.legend = TRUE,
           width = 1)+
  geom_text(aes(label = total_comments_month))+
  labs(x = NULL, y = NULL,
       title = "Last Month's Comments by Name/Status",
       subtitle = paste(last_month_day,"to",day, sep = " "))+
  coord_flip()+
  theme_classic()
p_active_month_names
```


```{r comment totals, echo=FALSE}
p_comment_total <- ggplot(data = recent_pull, aes(reorder(player_name, message_count), y = message_count, fill = status, label = message_count))+
  geom_col(show.legend = FALSE,width = 1)+
  geom_text(aes(label = message_count))+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Total Comments per User"))+
  coord_flip()+
  theme_classic()
p_comment_total
```
##Filesaving Processes
```{r,merge recruitlog and recent_pull, include=FALSE, echo = FALSE}
SGLCheatSheet <- semi_join(recent_pull,SGLRecruitLogMaster,by = "id")
SGLCheatSheet <- SGLCheatSheet %>% 
  select(id, player_name,user,status,message_count,recent_comments,date)
```

# The Non-Commenters Lists
Aims to create dataframe of everyone who has joined Discord, but capturing folks who have not commented also. 

```{r, noncommenters-list, echo = FALSE}
#Volunteers Commenters and NonCommenters 
vols_comment_and_non_commmenters <- REDCapData_Volunteers %>% 
  filter(discord_user != "NA") %>% 
  select(v_full_name,discord_user,discord_id,status,date_mod_training) %>% 
  mutate(redcap_project = "Volunteers")

patients_comment_and_non_commenters <- REDCapData_Patients %>% 
  fill(p_full_name,age) %>% 
  filter(discord_user != "NA") %>% 
  select(p_full_name,age,discord_user,id,status,date_recruited) %>% 
  mutate(minor_status = ifelse(age >= 18, "Adult", 
                               ifelse(age < 18, "Minor", NA))) %>% 
  mutate(redcap_project = "Patients")
#Match Variable Names 

```


```{r, slicetotals, echo = FALSE}
SGLCheatSheetSlice <- SGLCheatSheet %>% 
  group_by(player_name) %>% 
  arrange(desc(message_count)) %>% 
  filter(message_count > 25)

SGLComments <- ggplot(data = SGLCheatSheetSlice, aes(x = status, y = message_count, fill = status)) +
  geom_bar(stat = "identity", color ="black")
SGLComments <- SGLComments + labs(title="Streetlight Gaming League Discord Comments by Player Status", x = NULL, y = "Total Comments in Discord Server")+
  theme_classic()
SGLComments

TotalCommentStatusSummary <- SGLCheatSheet %>% 
  group_by(status) %>% 
  summarise(status_message_count = sum(message_count))
TotalCommentStatusSummary <- TotalCommentStatusSummary %>% 
  ungroup() %>% 
  mutate(total_messages = sum(status_message_count),
         percentage_messages = ((status_message_count/total_messages)*100))

totalstatustable <- gt(TotalCommentStatusSummary)
totalstatustable
#Now to do comments where it slices to only people with >50 comments
p_comment_total_slice <- ggplot(data = SGLCheatSheetSlice, aes(reorder(player_name, message_count), y = message_count, fill = status, label = message_count))+
  geom_col(show.legend = TRUE)+
  geom_text(aes(label = message_count))+
  labs(x = NULL, y = NULL) +
  ggtitle(paste("Total Comments per User"))+
  coord_flip()+
  theme_classic()
p_comment_total_slice
```

```{r filesaving, echo = FALSE}
currentDate <- Sys.Date()
dfFileName <- paste("SGLDataframe",currentDate,".Rdata", sep = "")
save.image(dfFileName)
```



```{r, counts, echo = FALSE}
#Counts
SGLRecruitLogMaster$status <- factor(SGLRecruitLogMaster$status)
StatusCount <- SGLRecruitLogMaster %>% 
  group_by(status) %>% 
  distinct(record_id, .keep_all = TRUE) %>% 
  tally()
gt(StatusCount)

```
Discords unmatched with redcap

```{r, NAs, echo = FALSE}
NACounter <- recent_pull %>% 
  select(record_id,user,id,status)%>% 
  filter(is.na(record_id)) %>% 
  filter(is.na(status)) %>% 
  distinct(id, .keep_all = TRUE)
print(NACounter)
```


```{r, patient-data-import-to-redcap, echo = FALSE}
patient_redcap_import <- datedtblnames %>% 
  select(record_id,user,id,message_count,date,last_date,last_message_count,recent_comments,time_interval,player_name) %>% 
  rename(
    comments_user = user,
    comments_id = id,
    comments_message_count = message_count,
    comments_date = date,
    comments_last_date = last_date,
    comments_last_message = last_message_count,
    comments_recent = recent_comments,
    comments_timeint = time_interval,
    comments_player_name = player_name
  ) %>%
  filter(record_id != "NA") %>% 
  mutate(redcap_repeat_instrument = "sgl_comments",
         sgl_comments_complete = "Complete")

patient_redcap_import <- patient_redcap_import %>%   
  group_by(record_id) %>% 
  arrange(comments_date) %>% 
  mutate(redcap_repeat_instance = seq_along(comments_date)) %>% 
  as.data.frame()
patient_redcap_import$comments_date <- as.character(patient_redcap_import$comments_date)
patient_redcap_import$comments_last_date <- as.character(patient_redcap_import$comments_last_date)
patient_redcap_import$comments_timeint <- as.character(patient_redcap_import$comments_timeint)

patient_redcap_import$comments_message_count <- as.double(patient_redcap_import$comments_message_count)



#in future workflow, at this point add a function that checks for duplicates with this patient_redcap_import file and the most recent redcap pull. Then, only upload differences. Will save considerable amount of time uploading 


importRecords(rcon,patient_redcap_import)
```


```{r, volunteer-data-import-to-redcap, echo = FALSE}
vol_and_staff <- c("Staff","Volunteer")
volunteer_redcap_import <- datedtblnames %>% 
  select(user,id,message_count,date,last_date,last_message_count,recent_comments,time_interval,player_name,status) %>% 
  rename(
    comments_user = user,
    comments_id = id,
    comments_message_count = message_count,
    comments_date = date,
    comments_last_date = last_date,
    comments_last_message = last_message_count,
    comments_recent = recent_comments,
    comments_timeint = time_interval,
    v_full_name = player_name,
  ) %>% 
  filter(status %in% vol_and_staff) %>% 
  rename(comments_status = status) %>% 
  mutate(redcap_repeat_instrument = "sgl_comments",
         sgl_comments_complete = "Complete")

#Reuploading REDCapData_Volunteers
vol_record_ids <- REDCapData_Volunteers %>% 
  select(v_full_name,record_id) %>%
  filter(v_full_name != "NA")
volunteer_redcap_import_record_ids <- stringdist_inner_join(volunteer_redcap_import,vol_record_ids, by = "v_full_name", max_dist = 0)

volunteer_redcap_import_record_ids <- volunteer_redcap_import_record_ids %>% 
  rename(comments_player_name = v_full_name.x) %>% 
  select(-v_full_name.y)

volunteer_redcap_import_record_ids <- volunteer_redcap_import_record_ids %>%   
  group_by(record_id) %>% 
  arrange(comments_date) %>% 
  mutate(redcap_repeat_instance = seq_along(comments_date)) %>% 
  as.data.frame()
volunteer_redcap_import_record_ids$comments_date <- as.character(volunteer_redcap_import_record_ids$comments_date)
volunteer_redcap_import_record_ids$comments_last_date <- as.character(volunteer_redcap_import_record_ids$comments_last_date)
volunteer_redcap_import_record_ids$comments_timeint <- as.character(volunteer_redcap_import_record_ids$comments_timeint)

volunteer_redcap_import_record_ids$comments_message_count <- as.double(volunteer_redcap_import_record_ids$comments_message_count)



#in future workflow, at this point add a function that checks for duplicates with this volunteer_redcap_import_record_ids file and the most recent redcap pull. Then, only upload differences. Will save considerable amount of time uploading 



importRecords(vcon,volunteer_redcap_import_record_ids)

```

```{r, cheatshee,t, echo = FALSE}
REDCapData_Patients <- exportRecords(rcon,labels = FALSE)

sgl_status_df <- REDCapData_Patients %>% 
  select(record_id,p_full_name,age,discord_invite_status,sgl_creed_status,sgl,discord_user,comments_user,redcap_repeat_instrument,redcap_repeat_instance)

# Lists all folks who have been designated as set up in Discord-- this includes ppl with confirmed by staff usernames (reading their name in the welcome message upon entry), or comment history in server. 

all_discord_users_sheet <- sgl_status_df %>% 
  filter(unclass(discord_invite_status) == 1) %>% 
  distinct(record_id,p_full_name,age,sgl_creed_status,sgl)


# Need to be able to pull the most recent discord user from the comment_user column, and for discord_user in sgl new patient form. This code modified from Census. 

current_discord_info <- sgl_status_df %>% 
  group_by(record_id) %>% 
  filter(redcap_repeat_instrument == "sgl_new_patient") %>% 
  mutate(current_discord_info = last(discord_user,order_by = redcap_repeat_instance)) %>% 
  fill(current_discord_info) %>% 
  distinct(record_id, .keep_all = TRUE) %>% 
  dplyr::select(record_id,current_discord_info)

current_discord_comment <- sgl_status_df %>% 
  group_by(record_id) %>% 
  filter(redcap_repeat_instrument == "sgl_comments") %>% 
  mutate(current_discord_user = last(comments_user,order_by = redcap_repeat_instance)) %>% 
  fill(current_discord_user) %>% 
  distinct(record_id, .keep_all = TRUE) %>% 
  dplyr::select(record_id,current_discord_user)

all_discords_user_info_sgl_new <- left_join(all_discord_users_sheet, current_discord_info, by = "record_id")

all_discords_user_info_sglnew_and_comments <-   left_join(all_discords_user_info_sgl_new, current_discord_comment, by = "record_id")

VolToken <- read_csv("volunteertoken.csv", col_names = FALSE)
StreetlightVolunteerToken <- as.character(VolToken[1,1])
vcon <- redcapConnection(redcap_api_url, token = StreetlightVolunteerToken)
REDCapData_Volunteers <- exportRecords(vcon,labels = FALSE)

vol_discord_info <- REDCapData_Volunteers %>% 
  group_by(record_id) %>% 
  fill(v_full_name,status) %>% 
  filter(redcap_repeat_instrument == "sgl_new_patient") %>% 
  mutate(current_discord_info = last(discord_userr,order_by = redcap_repeat_instance)) %>% 
  fill(current_discord_info) %>% 
  distinct(record_id, .keep_all = TRUE) %>% 
  dplyr::select(record_id,v_full_name,status,current_discord_info)


vol_comments <- REDCapData_Volunteers %>% 
  group_by(record_id) %>% 
  filter(redcap_repeat_instrument == "sgl_comments") %>% 
  mutate(current_discord_user = last(comments_user,order_by = redcap_repeat_instance)) %>% 
  fill(current_discord_user) %>% 
  distinct(record_id, .keep_all = TRUE) %>% 
  dplyr::select(record_id,current_discord_user)

volunteer_discord_list <- full_join(vol_discord_info,vol_comments, by = "record_id") %>% 
  rename(user_from_redcap = current_discord_info,
         user_from_comments = current_discord_user) %>% 
   mutate(commented = case_when(is.na(user_from_comments) ~ "No",
                               TRUE ~ "Yes"))

patient_discord_info <-  all_discords_user_info_sglnew_and_comments %>% 
  mutate(status = "Patient") %>% 
  rename(user_from_redcap = current_discord_info,
         user_from_comments = current_discord_user) %>% 
  mutate(commented = case_when(is.na(user_from_comments) ~ "No",
                               TRUE ~ "Yes"))



write_csv(patient_discord_info, "patient_cheatsheet.csv", na = "")
write_csv(volunteer_discord_list, "volunteer_cheatsheet.csv", na = "")

```

